A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Parse

\begin{lstlisting}
> r <- 5
> env <- new.env()
> env$r <- 9
> eval(r, envir = env)
[1] 5
> evalq(r, envir = env)
[1] 9
\end{lstlisting}

@@

Although \c{eval} takes an R expression, it can evaluate a string if this string is first parsed with \c{parse}, \c{str2expression} or \c{str2lang}. This happens for \PercentParsedEvals of the eval calls, and \PercentParsedCallSites of the call sites.

>>>>

\begin{lstlisting}
> r <- 5
> env <- new.env()
> env\$r <- 9
> eval(r, envir = env)
[1] 5
> evalq(r, envir = env)
[1] 9
\end{lstlisting}

@@

\c{eval} takes an R expression. To evaluate a string, it first has to be parse
using either \c{parse}, \c{str2expression} or \c{str2lang} functions. The
difference between them is that the latter two are specialized versions of
\c{parse} that do not keep source references (line and column numbers). This
happens for \PercentParsedEvals of the eval calls, and \PercentParsedCallSites
of the call sites. The input to \c{parse} can come from either a string, a file
or directly a from a user input in interactive REPL session\footnote{in the
  corpus, there is only one call site to eval that takes parse expression from a
  user input, \c{invokeRestartInteractively} that prompts user for new argument
  values when a function invocation fails.}.
